My title

### 2024-09-23 paper/paper.qmd
Forgot to commit these two from last commit, oops!

---
title: "My title"
subtitle: STA304 Paper 1 Submission
author: 
  - Veyasan Ragulan
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

analysis_data |> 
  ggplot(mapping = aes(x = botanical_name)) +
  geom_bar() +
  theme_minimal() +
  labs(x = "Tree species",
       y = "Number of trees planted")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

>>>>

---
title: "My title"
subtitle: STA304 Paper 1 Submission
author: 
  - Veyasan Ragulan
  - Another author
thanks: "Code and data are available at: https://github.com/Veyasan1/STA3014-Paper1"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Urban spaces are often void of nature, whether it be grass fields, blooming flowers, or teaming and diverse natural wildlife. One simple way to tackle this is to incorporate nature within the urban landscape, such as with trees. Trees are a vital plant in the world, they take in carbon dioxide and provide oxygen, a key component in the air we breath. Urban areas are known for the excess in carbon dioxide, which only makes it seem natural that trees can live and perhaps thrive in such environments. Trees can also alter the way wind affects pedestrians below (@beptree). It should be no suprise then, that many cities around the world, including Toronto, have incorporated trees into their landscape, in busy downtown centres, to sleepy suburbs, and everywhere in between.

@@

The data comes from OpedData Toronto, an open source portal containng datasets carried out at the municipal level (@opendata). This particular dataset is called Street Tree Data, and focuses on city-owned trees located on roads. This information would be most likely used by city planners and road maintenance, ensuring snow plows and street dusters don't impede on any trees that line the roads. It is important to not that there may be some privately owned trees listed among the municipal trees, as they may be of interest with regards to road maintenance or other city services.

@@

```{r}
#| label: fig-topspecies
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

top_species_count <- analysis_data %>%
  count(botanical_name, sort = TRUE) %>%
  head(10)

top_species_count |> 
  ggplot(aes(y = botanical_name, x = n)) +
  geom_col() +
  theme_minimal() +
  labs(x = "Planted Trees",
       y = NULL)
```
Talk way more about it.

```{r}
#| label: fig-ward
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

ward_count <- analysis_data %>%
  count(ward, sort = TRUE) %>%
  head(10)

ward_count |> 
  ggplot(aes(x = ward, y = n)) +
  geom_col() +
  theme_minimal() +
  labs(x = "Ward",
       y = "Number of trees planted")
```

```{r}
#| label: fig-speciesward
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

top_species_ward_count <- analysis_data %>%
  filter(botanical_name == "Acer platanoides") %>%
  count(ward, sort = TRUE) %>%
  head(10)

top_species_ward_count |> 
  ggplot(aes(x = ward, y = n)) +
  geom_col() +
  theme_minimal() +
  labs(x = "Ward",
       y = "Number of trees planted")
```
```{r}
#| label: fig-trunk
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

max_dbh <- analysis_data %>%
  filter(dbh_trunk == 815)

max_dbh

analysis_data |> 
  ggplot(mapping = aes(x = dbh_trunk)) +
  geom_histogram() +
  theme_minimal() +
  labs(x = "DBH Diameter",
       y = "Tree Count")
```
